---
title: "SAN 2021 Annual Meeting Presentation"
author: "Aleru"
date: "5/26/2021"
output:
  html_document:
    df_print: paged
subtitle: Details the data pre-processing and analysis for the presentation given
  E-Social event 'Co-authorship network structure and gender inequalities of the Argentine
  neuroscientific community'
  in the [SAN 2021 Meeting](https://san2021.saneurociencias.org.ar/) as part of the
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```

# Data Preparation

```{r librerias, include=FALSE}
library(tidyverse)
library(GGally)
library(gplots)
library(igraph)
library(stringi)
library(ggpubr)
library(ggfortify)
library(corrplot)
```

## Data loading

We load the required datasets from different sources. 

```{r dataset_loading}

#Load the dataset containing the matched names
matchees <- read_csv('Scraper/Scraped_datasets/matche_nombres.csv') %>% 
  #Get rid of missing values
  drop_na(messy)

#Load the dataset containing the reference of the numeric indicator variable for sex
sexo_ref <- read_csv('mincyt_datasets/ref_sexo.csv')

#Load the dataset containing the reference of the numeric indicator variable for conicet category
categoria_ref <- read_csv2('mincyt_datasets/ref_categoria_conicet.csv')

#Load the dataset containing conicet staff
personas_actual <- read_csv2('mincyt_datasets/personas_2018.csv') %>% 
  inner_join(.,categoria_ref)  #Join the dataset with the one containing the numeric indicator reference for conicet category 

#Load people database
personas <- read_csv2('mincyt_datasets/personas.csv')

# Load the dataframe holding the authors posters names, poster title and year
posters <- read_csv('Scraper/Scraped_datasets/all_posters.csv')
#Generate a unique id for every entry
posters$poster_author_id <- 1:nrow(posters)
#Create one dataframe to hold name and poster title for first authors and one for last authors
first_authors <- posters %>% drop_na(titulo) %>% group_by(titulo) %>% summarize(first(autor)) %>% ungroup() %>% mutate(author_position = 'first') %>% rename(name = `first(autor)`)
last_authors <- posters %>% drop_na(titulo) %>% group_by(titulo) %>% summarize(last(autor)) %>% ungroup() %>% mutate(author_position = 'last') %>% rename(name = `last(autor)`)
#Combine the two dataframes
binded_positions <- rbind(first_authors, last_authors)
#Use previously created dataframes to add a column to the posters dataframe containing author position
posters <- left_join(posters, binded_positions, by = c('autor' = 'name', 'titulo' = 'titulo'))
#Other positions
posters <- posters %>% replace_na(list(author_position = 'other'))
```

## Filter name matches

Filter the authors matching names dataframe by the KNN distance score according to the 1th percentile and a WRatio score higher or equal to 95.

```{r}
#Get the 1th percentile value for the KNN distance score
percent1 <- quantile(
  matchees$score[matchees$score > 0], #Calculate over KNN distance score excluding 0 values
  0.01
)
#Filter the matchees dataset
filter_match <- matchees %>% filter(score < percent1 & WRatio >= 95)
```


## Data Transformations

```{r}
#Create a new factor column with an abbreviated conicet category for PIs 
personas_actual$categoria_conicet_refactor <-  fct_collapse(personas_actual$categoria_conicet_descripcion,
             becario = 'Becario doctoral',
             posdoc = 'Becario postdoctoral',
             investigador_low = c('Investigador adjunto', 'Investigador asistente'),
             investigador_high = c('Investigador independiente', 'Investigador principal', 'Investigador superior'),
             otros = c('No pertenece a Conicet', 'Otro personal Conicet', 'Personal de apoyo')
             )

#Create a new factor column (binary) to specify researcher status
personas_actual$investigador <- fct_collapse(personas_actual$categoria_conicet_descripcion,
                                             no_inv = c('becario','posdoc','otros'),
                                             inv = c('investigador_low','investigador_high')
                                            )

#Create a new column combining the name and the last name and removing foreign characters
personas$nuevo_nombre <- str_to_lower(
  stri_trans_general(
  str = paste(personas$nombre, personas$apellido),
  id = 'Latin-ASCII')
)

#Join the people database with the conicet staff dataset using the person id 
personas <- left_join(
  personas,
  personas_actual %>% select(persona_id, categoria_conicet_descripcion, investigador)
)

#Transform labels from the sex factor column
personas$sexo_id <- fct_recode(factor(personas$sexo_id), Female = '1', Male = '2')

# Redefine topics to collapse common categories and generate a new topic factor
posters$topic <-  fct_collapse(
  posters$tema,
  `Theoretical and Computational Neuroscience` = c('Theoretical and Computational Neuroscience', 'Computational Neuroscience'),
  BAW = c('BAW', 'Brain Awareness Week Activities'),
  `Cellular and Molecular Neurobiology` = c('Cellular and Molecular Neurobiology', 'Cellular and Molecular neurobiology'),
  `Cognition, Behavior and Memory` = c('Cognition, Behavior and Memory', 'Cognition, Behavior, and Memory'),
  `Sensory and Motor Systems` = c('Sensory and Motor Systems', 'Motor Systems', 'Sensory Systems'),
  `Synaptic Transmission and Excitability` = c('Synaptic Transmission and Excitability', 'Neural excitability, synaptic transmission and neuron-glia interactions'),
  `Neural Circuits and Systems Neuroscience` = c('Neural Circuits and Systems Neuroscience', 'Neural Circuit Physiology', 'Integrative Systems')
  )

# Drop erroneous detected topics

posters <- posters[!str_detect(posters$tema, 'P\\d+'),]


#Join the dataframe with the poster information with the dataframe containing the filtered name matches 
joined_authors <- inner_join(posters,
          filter_match %>% select(match, original, id),
          by = c('autor' = 'original')) %>%
  left_join(.,
            personas,
            by = c('id'='persona_id'))

#Generate new row id
joined_authors$row_id <- 1:nrow(joined_authors)

#Drop duplicates
joined_authors <- joined_authors %>% distinct(autor, titulo, .keep_all = TRUE)
```

# Sex comparisons

These comparisons seek to explore the differences in sex proportion within posters authors.

## Sex over the years

We try to observe differences in the proportion of women over the years. However many times the same person can appear in several posters thus accounting for more than one entry for their respective sex. Therefore we create two plots, one with repeated authors and the second one without duplicates.

Both plots show women proportion, the 95% confidence interval, the total amount of authors for that year and the 95% interval for a binomial distribution with *p* equal to 0.5 and *n* equal to the amount of total authors. Moreover for the second plot without duplicates, the overall women proportion for all years is shown as a red dotted line. Lastly, we show the probability of observing the women proportion over each year as given by the following binomial distribution.

$P_{x} = \binom{n}{x} 0.5^{x} 0.5^{n-x}$

Where *n* is the total amount of authors and *x* is the total of women with a probability of success of 0.5.  


```{r}
sex_by_year <- function(dataset){
  dataset %>% count(year, sexo_id) %>% pivot_wider(names_from = sexo_id, values_from = n) %>% 
  mutate(total = Female + Male,
        female_prop = Female/total,
         male_prop = Male/total,
        low_ci = female_prop - sqrt(female_prop*(1 - female_prop)/total) * 1.96,
        high_ci = female_prop + sqrt(female_prop*(1 - female_prop)/total) * 1.96,
        low_bi = qbinom(0.975, total, 0.5)/total,
        high_bi = qbinom(0.025, total, 0.5)/total,
        prob = round(1 - pbinom(Female, total, 0.5), 3)
  )
}

non_unique_authors <- sex_by_year(joined_authors)

unique_authors <- sex_by_year(
  joined_authors %>% distinct(match, .keep_all = TRUE)
) 
  
ggplot(data = non_unique_authors, mapping = aes(x = year, y = female_prop)) +
  geom_rect(aes(xmin = year - 0.5, xmax = year + 0.5, ymin = low_bi, ymax = high_bi), fill = 'lightgrey', alpha = 0.5) +
  geom_line() +
  geom_text(aes(label = prob, y = high_ci + 0.01)) +
  geom_errorbar(aes(ymin = low_ci, ymax = high_ci), width = 0.35) +
  geom_point(aes(size = total), shape = 1) +
  theme_pubclean() +
  labs(title = 'Sex proportion over years (with duplicates)') + xlab('Year') + ylab('Proportion of women') +
  scale_size(name = 'Total authors') 

ggplot(data = unique_authors, mapping = aes(x = year, y = female_prop)) +
  geom_rect(aes(xmin = year - 0.5, xmax = year + 0.5, ymin = low_bi, ymax = high_bi), fill = 'lightgrey', alpha = 0.5) +
   geom_hline(yintercept = sum(unique_authors$Female)/sum(unique_authors$Female, unique_authors$Male),
             linetype = 'dashed', color = 'red') +
  geom_line() +
  geom_text(aes(label = prob, y = high_ci + 0.02)) +
  geom_errorbar(aes(ymin = low_ci, ymax = high_ci), width = 0.35) +
  geom_point(aes(size = total), shape = 1) +
  theme_pubclean() +
  labs(title = 'Sex proportion over years') + xlab('Year') + ylab('Proportion of women') +
  scale_size(name = 'Total authors') 
```


## Sex by topic

In this case we wish to examine the proportion for each sex by poster topic. To create the plot some topics were collapsed and merged together due to changes in the poster topics over the years. Next we detail those topics which are made up of several themes.

* `Theoretical and Computational Neuroscience`: Esta compuesta por *'Theoretical and Computational Neuroscience'* y *'Computational Neuroscience'*
* `BAW`: Esta compuesta por *'BAW'* y *'Brain Awareness Week Activities'*
* `Sensory and Motor Systems`: Esta compuesta por *'Sensory and Motor Systems'*, *'Motor Systems'* y *'Sensory Systems'*
* `Synaptic Transmission and Excitability`: Esta compuesta por *'Synaptic Transmission and Excitability'*, *'Neural excitability'* y *'synaptic transmission and neuron-glia interactions'*
* `Neural Circuits and Systems Neuroscience`: Esta compuesta por *'Neural Circuits and Systems Neuroscience'*, *'Neural Circuit Physiology'* e *'Integrative Systems'*

The plot shows with the colored bars the sex proportion and uses dots to reflect a proportion of 0.5 as well as the total number of authors for each topic given by the dot size. Furthermore the lines extending from the dots form the 95% interval for a binomial distribution with an *n* equal to the number of authors in every topic with a probability of success of 0.5

```{r}
#Generates a 95% confidence interval for every topic using a binomial distribution of n equal to the n of that topic and a probability of 0.5
sex_by_topic <- joined_authors %>% group_by(topic) %>% distinct(match) %>% count(topic) %>% ungroup() %>%
    mutate(
      low_bi = qbinom(0.025, n, 0.5)/n,
      high_bi = qbinom(0.975, n, 0.5)/n
           )

ggplot(data = joined_authors, mapping = aes(x = topic, fill = sexo_id)) +
  geom_bar(position = 'fill') +
  geom_pointrange(data = sex_by_topic, aes(x = topic, y = 0.5, ymin = low_bi, ymax = high_bi, size = n), inherit.aes = FALSE) +
  scale_x_discrete(labels = str_sub(unique(joined_authors$topic), end = 20)) +
  coord_flip() + scale_size(name = 'Total authors', range = c(0.5,1.5)) +
  xlab('Topic') + ylab('Proportion') +
  scale_fill_brewer(name = 'Sex', palette = 'Set1') + theme_pubclean()
```
## Sex proportion and conicet category

```{r}
sex_category <- joined_authors %>% filter(categoria_conicet_descripcion != 'No pertenece a Conicet' & categoria_conicet_descripcion != 'Personal de apoyo'
) %>% arrange(year) %>% distinct(match, .keep_all = TRUE)
ggplot(data = sex_category, mapping = aes(x = categoria_conicet_descripcion, fill = sexo_id)) +
  geom_bar(position = 'fill') +
  coord_flip() + scale_size(name = 'Total authors', range = c(0.5,1.5)) +
  xlab('Research status') + ylab('Proportion') +
  scale_fill_brewer(name = 'Sex', palette = 'Set1') + theme_pubclean()
```

## Sex proportion author order

The following analysis explore the relationship between the sex proportion and the author order

### Sex proportion author order by year

The colored bars represent the sex proportion for each year for each poster author position. The dashed line represents the 0.5 proportion. 

```{r, warning=FALSE}
plus2authors <- joined_authors %>% group_by(titulo) %>% filter(n() >= 2) %>% ungroup()
ggplot(data = plus2authors, mapping = aes(x = year, fill = sexo_id)) +
  geom_bar(position = 'fill') +
  geom_hline(yintercept = 0.5, linetype = 'dashed') +
  stat_prop(geom = 'label', aes(label = round(..prop.., 2), by = year), size = 3.5) +
  facet_wrap(~author_position, labeller = labeller(author_position = c('first' = 'First', 'last' = 'Last', 'other' = 'Other'))) +
  theme_pubclean() +
  xlab('Year') + ylab('Proportion') + scale_fill_brewer(name = 'Sex', palette = 'Set1')
```


### Gender proportion author order with intervals

```{r, warning=F, message=F}
plus2authors %>% group_by(year, author_position) %>% 
  summarise(
    media = mean(sexo_id == 'Female'), 
    conteo = n(), 
    ci_up = media + (2 * sqrt(media*(1-media)/conteo)),
    ci_low = media - (2 * sqrt(media*(1-media)/conteo)),
    binom_low = qbinom(0.025, conteo, 0.5)/conteo,
    binom_up = qbinom(0.975, conteo, 0.5)/conteo
      ) %>% 
  filter(author_position != 'other') %>%
  ggplot(mapping = aes(x = year, y = media, shape = author_position)) +
  geom_rect(aes(ymin = binom_low, ymax = binom_up, xmax = year - 1, xmin = year), fill = 'lightgrey',alpha = .25, position = position_dodge(.75)) +
  geom_hline(
    yintercept = c(
      table(plus2authors$sexo_id[plus2authors$position == 'first'])[['Female']]/sum(table(plus2authors$sexo_id[plus2authors$position == 'first'])),
      table(plus2authors$sexo_id[plus2authors$position == 'last'])[['Female']]/sum(table(plus2authors$sexo_id[plus2authors$position == 'last']))
    ),
    linetype = 'dashed',
    color = RColorBrewer::brewer.pal(3, 'Set1')[1:2]
  ) +
  geom_hline(yintercept = 0.5, linetype = 'dashed') +
  geom_line(position = position_dodge(.75)) +
  geom_errorbar(aes(ymax = ci_up, ymin = ci_low, color = author_position), width = .2, position = position_dodge(.75)) +
  geom_point(aes(color = author_position), size = 5, position = position_dodge(.75)) +
  theme_pubclean() +
  theme(legend.position = 'bottom') + xlab('Año') + ylab('Proporcion de mujeres') +
  scale_shape_discrete(name = 'Posicion de la autoria', labels = c('Primera','Ultima')) +
  scale_color_brewer(name = 'Posicion de la autoria', labels = c('Primera', 'Ultima'), palette = 'Set1')
```

## Hypothesis testing analysis

### Gender proportion

```{r}
proporcion_sexo_total <- joined_authors %>% distinct(match, .keep_all = T) %>% count(sexo_id) %>%
  mutate(
  bi_low = quantile(rbinom(10000, sum(n), 0.5), probs = 0.025),
  bi_high = quantile(rbinom(10000, sum(n), 0.5), probs = 0.975),
  sqd = (n - (sum(n)/2))^2,
  chisqd = sqd/(sum(n)/2)
    )

proporcion_sexo_total
```

Es util comparar las proporciones observadas con las esperadas utilizando el estadistico $\chi^{2}$ donde la probabilidad de las proporciones observadas segun el estadistico chi-cuadrado es `r pchisq(q = sum(proporcion_sexo_total$chisqd), 1, lower.tail = F)`


### Gender and position, two-way contingency table


```{r}
tabla_frecuencia_sexo <- xtabs(~ sexo_id + author_position, data = plus2authors %>% filter(author_position != 'other'))

tabla_frecuencia_sexo

chisq.test(
  tabla_frecuencia_sexo
)

chisq.test(
  tabla_frecuencia_sexo
)$stdres

rcompanion::cramerV(
  as.matrix(tabla_frecuencia_sexo),
  ci = TRUE,
  bias.correct = TRUE
)
```

Se puede observar mejor esta relacion con un grafico de mosaico

```{r}
vcd::mosaic(tabla_frecuencia_sexo, gp = vcd::shading_hcl, gp_args = list(interpolate = c(1, 1.8)))
```


## Bayesian Approach

```{r}
non_unique_authors %>%
  mutate(
    independent_median = qbeta(c(0.5), Female + 1, total - Female + 1),
    independent_low = qbeta(c(0.025), Female + 1, total - Female + 1),
    independent_high = qbeta(c(0.975), Female + 1, total - Female + 1)
  ) %>%
  ggplot(mapping = aes(x = year, y = independent_median, ymin = independent_low, ymax = independent_high)) +
  geom_line() +
  geom_point(size = 3) +
  geom_errorbar(width = 0.3) +
  ylab('Median of the parameter distribution') + xlab('Year')
```

## Probability analysis

We are interested in the probability of being a female first author given that the last author is male and the other way around. To determine this we first have to determine prior probabilities. First of all 

What is the probability that someone is a first author? $P(First \ Author)$ = `r sum(plus2authors$author_position == 'first')/nrow(plus2authors)`

The probability of someone being a last author is exactly the same as the one above given that all posters necessarily have a first and last author. 

What are the odds of being a first author? $odds = \frac{P(First \ Author)}{P(\neg First \ Author)}$ = `r (sum(plus2authors$author_position == 'first')/nrow(plus2authors))/(1-(sum(plus2authors$author_position == 'first')/nrow(plus2authors)))`

After establishing the prior probabilities for the authors positions we examine the sex proportions.

What is the probability that someone is female? $P(Female)$ = `r sum(plus2authors$sexo_id == 'Female')/nrow(plus2authors)`

Thus, the probability of being a male is $1 - P(Female)$. To see how the author position and the sex of the author relate to each other we examine the joint probability.

What is the probability of being both a first author and a female? $P(Female \cap First \ Author)$ = `r sum(plus2authors$sexo_id == 'Female' & plus2authors$author_position == 'first')/nrow(plus2authors)`

What is the probability of being both a first author and a male? $P(Male \cap First \ Author)$ = `r sum(plus2authors$sexo_id == 'Male' & plus2authors$author_position == 'first')/nrow(plus2authors)`

What is the probability of being both a last author and a female? $P(Female \cap Last \ Author)$
`r sum(plus2authors$sexo_id == 'Female' & plus2authors$author_position == 'last')/nrow(plus2authors)`

What is the probability of being both a last author and a male? $P(Male \cap Last \ Author)$
`r sum(plus2authors$sexo_id == 'Male' & plus2authors$author_position == 'last')/nrow(plus2authors)`

Now the question can be about how the fact of being a Female affects the probability of being a last author. 

What is the probability of being a last author given one is female? $P(Last \ Author|Female) = \frac{P(Female \cap Last \ Author)}{P(Female)}$ 

`r sum(plus2authors$sexo_id == 'Female' & plus2authors$author_position == 'last')/sum(plus2authors$sexo_id == 'Female')`

Furthermore we could calculate the odds ratio for female as last author `r xtabs(~sexo_id + author_position, plus2authors)[1,2]/sum(xtabs(~sexo_id + author_position, plus2authors)[1,c(1,3)])` and male as last author `r xtabs(~sexo_id + author_position, plus2authors)[2,2]/sum(xtabs(~sexo_id + author_position, plus2authors)[2,c(1,3)])`. We could now ask about the odds ratio which is equal to the odds of being a last author while female and the odds of being a last author while male. To calculate this and get uncertainty bounds, we compute the mean and confidence interval via bootstraping.

```{r}
#Repeat the process 10.000 times and get 95% interval
res <- replicate(10000,
          {
            n_df <- nrow(plus2authors)
            #Sample n numbers from n possible numbers where n is the row number from the dataset
            sampled_authors <- sample(n_df, n_df, replace = TRUE)
            #Generate dataframe with the rows corresponding to the sampled numbers
            sampled_df <- plus2authors[sampled_authors, ]
            #Frequency Table
            sampled_freq <- xtabs(~sexo_id + author_position, sampled_df)
            (sampled_freq[2,2]*sum(sampled_freq[1,c(1,3)]))/(sampled_freq[1,2]*sum(sampled_freq[2,c(1,3)]))
          }
)
mean(res)
quantile(res, c(.025,.975))
```
As a follow up we would like to know how the sex of the last author affects the sex of the first author. 


```{r}
#Last author is female
female_last <- plus2authors %>% filter(
  titulo %in% plus2authors[which(plus2authors$sexo_id == 'Female' & plus2authors$author_position == 'last'),'titulo']$titulo
)

#Last author is male
male_last <- plus2authors %>% filter(
  titulo %in% plus2authors[which(plus2authors$sexo_id == 'Male' & plus2authors$author_position == 'last'),'titulo']$titulo
)

freq_tab <- cbind(
  table(female_last[female_last$author_position == 'first',]$sexo_id),
  table(male_last[male_last$author_position == 'first',]$sexo_id)
)
rownames(freq_tab) <- c('Female First', 'Male First')
colnames(freq_tab) <- c('Female Last', 'Male Last')
freq_tab
```
The odds for a female first author when the last author is female are `r freq_tab[1,1]/freq_tab[2,1]`, the odds for a female first author when the last author is male are `r freq_tab[1,2]/freq_tab[2,2]`. The odds ratio is `r (freq_tab[1,1]*freq_tab[2,2])/(freq_tab[2,1]*freq_tab[1,2])`.

# Graph Analysis

```{r}
joined_authors <- joined_authors %>% drop_na(titulo)
bipartite_san <- graph.data.frame(joined_authors[c('titulo','match','year','tema')], directed = F)
V(bipartite_san)$type <- V(bipartite_san)$name %in% joined_authors$match
#Get graph data for each year graph
df_year_san <- tibble( #Empty dataframe to hold the results of the for loop
  size = NA, #Graph size
  mean_short_path = NA, #Average shortest path length
  density = NA, #Largest component graph density
  no_comp = NA, #Number of components
  max_comp = NA, #Size of the maximum component
  diameter = NA, #Largest component graph diamaeter
  transitivity = NA, #Largest component graph transitivity,
  year = NA 
) 
#Iterate over each year to calculate a graph (and associated measures) for that year's conference
for(y in unique(joined_authors$year)){
  #Create a graph from the edge list of the year y
  year_san <- joined_authors %>% filter(year == y) %>%
    select(titulo,match,tema) %>%
    graph.data.frame(., directed = F) 
  #Transform the graph into a bipartite graph
  V(year_san)$type <- V(year_san)$name %in% joined_authors[joined_authors$year == y,'match'][[1]]
  #Project the bipartite graph to get the authors graph
  bn_year_san <- bipartite.projection(year_san)[[2]]
  #Add the sex attribute to the vertices
  V(bn_year_san)$sex <- joined_authors %>% filter(match %in% V(bn_year_san)$name) %>% distinct(match, .keep_all = T) %>% 
    select(sexo_id) %>% .[[1]]
  #Get the name of the largest component
  year_lg_comp <- names(
    sort(
      table(
        components(bn_year_san)[[1]]
            )
            ,decreasing = T)
                  )[1]
  #Create a subgraph consisting of the nodes of the largest component
  bn_year_large <- induced_subgraph(
    bn_year_san, 
    which(
      components(bn_year_san)[[1]] == year_lg_comp
      )
    )
  df_year_san <- df_year_san %>%
    add_row(
      size = gsize(bn_year_san),
      mean_short_path = average.path.length(bn_year_large),
      density = edge_density(bn_year_large),
      no_comp = components(bn_year_san)$no,
      max_comp = max(components(bn_year_san)$csize),
      diameter = diameter(bn_year_large, directed = F, weights = NULL),
      transitivity = transitivity(bn_year_large, type = 'global', weights = NULL),
      year = y
    )
}
df_year_san <- df_year_san %>% drop_na()

attrb_names <- c('Size', 'Mean Short Path', 'Density', '# of Components', 'Max. Component size', 'Diameter', 'Transitivity')
```

These analysis were done using the most stringent threshold criteria thus leaving only `r length(unique(filter_match$match))` unique authors. 

## Authors Graph

```{r}
# Use the second projection (containing the authors) from the bipartite graph
grafo_autores <- bipartite.projection(bipartite_san)[[2]]

# Add sex attribute to the vertices of the authors graph
grafo_autores <- set.vertex.attribute(grafo_autores,
                                      name = 'sex',
                                      value = joined_authors %>% distinct(match, .keep_all = T) %>% select(sexo_id) %>% .[[1]] 
                                        )  

# Add category attribute to the vertices of the authors graph
grafo_autores <- set.vertex.attribute(grafo_autores,
                                      name = 'category',
                                      value = joined_authors %>% distinct(match, .keep_all = T) %>% select(categoria_conicet_descripcion) %>% .[[1]]
                                        )

grafo_autores_large <- induced_subgraph(grafo_autores, vids = which(components(grafo_autores)$membership == 1))
```


### Circle

```{r, fig.height=10}
plot(grafo_autores, vertex.label = NA, vertex.size = 1, layout = layout_in_circle(grafo_autores), vertex.color = c('red','blue')[V(grafo_autores)$sex])
```

### Fruchterman-Reingold

```{r, fig.height=10}
plot(grafo_autores, vertex.label = NA, vertex.size = 1, layout = layout_with_fr(grafo_autores, niter = 1000), vertex.color = c('red','blue')[V(grafo_autores)$sex])
```

### Kamada Kawai

```{r, fig.height=10}
plot(grafo_autores, vertex.label = NA, vertex.size = 1, layout = layout_with_kk(grafo_autores), vertex.color = c('red','blue')[V(grafo_autores)$sex])
```


### Graph characteristics

There are `r components(grafo_autores)$no` components in the graph with a median value of `r median(components(grafo_autores)$csize)` and a size range going from `r range(components(grafo_autores)$csize)[1]` to `r range(components(grafo_autores)$csize)[2]`.

### Components Distribution

```{r}
hist(
  components(grafo_autores)$csize,
  main = 'Components size distribution',
  xlab = 'Number of components'
)
```

### Components Distribution (withouth the largest component)

```{r}
hist(
  components(grafo_autores)$csize[components(grafo_autores)$csize < max(components(grafo_autores)$csize)],
  main = 'Components size distribution',
  xlab = 'Number of components'
)
```

### Graph attributes through time

```{r}
colnames(df_year_san) <- c(attrb_names, 'Year')
df_year_san %>%
  pivot_longer(!Year, names_to = 'attributes') %>%
ggplot(mapping = aes(x = Year, y = value)) +
  geom_point() +
  geom_line() +
  facet_wrap(~attributes, scales = 'free_y') +
  theme_classic()

graph_correlation <- df_year_san %>% select(-Year) %>% cor() 
rownames(graph_correlation) <- attrb_names
colnames(graph_correlation) <- attrb_names
corrplot(graph_correlation, 'color', addCoef.col = 'black', tl.col = 'black', number.cex = 0.75, order = 'hclust', diag = FALSE, addrect = 2)
```



